---
title: "Regenerative Injections for Joint Hypermobility: A Reproducible Evidence Map and Meta-Analysis"
author: "Phillips Le"
date: today
format:
  html:
    toc: true
    code-fold: true
    embed-resources: true
execute:
  warning: false
  message: false
---

## Summary

This report synthesizes the published evidence on regenerative injections
(dextrose prolotherapy and platelet-rich plasma, PRP) for joint hypermobility,
including hypermobile Ehlers–Danlos syndrome (hEDS). It has two parts: a
**targeted meta-analysis** of the small subset of studies that are comparable
enough to pool (the TMJ prolotherapy RCTs), and an **evidence map** of the wider,
un-poolable literature. The honest headline: the evidence base is small,
lopsided (controlled trials exist only for the jaw), and largely uncontrolled
elsewhere.

> This is a scoping-level synthesis by a student, not a definitive efficacy
> verdict, and not medical advice.

## Data

```{r}
library(readr)
library(dplyr)
studies <- read_csv("../data/raw/studies.csv", show_col_types = FALSE)
knitr::kable(studies |> select(authors, year, joint, intervention, design, n, direction, quality))
```

## Part 1 — Meta-analysis (poolable subset)

Real, cited effect sizes (see `R/01_meta_analysis.R` and `data/raw/pooled_results.csv`).
Independent meta-analyses agree dextrose prolotherapy reduces TMJ pain vs placebo:
Sit et al. 2021 pooled SMD −0.76 (95% CI −1.19 to −0.32), I²=0%
(doi:10.1038/s41598-021-94119-2); Nagori et al. 2018 pain MD −1.00 and mouth-opening
MD −3.32 (doi:10.1111/joor.12698). Effects on mouth opening/function are inconsistent,
evidence quality is low–moderate, and follow-up is short. All TMJ (jaw) only.

```{r}
#| eval: false
source("../R/01_meta_analysis.R")
```

## Part 2 — Evidence map (whole literature)

Studies that cannot be pooled are mapped instead: which joints, which
interventions, how strong. Gaps in the grid are where evidence is missing.

```{r}
#| fig-width: 9
#| fig-height: 5
source("../R/02_evidence_map.R")
```

## Interpretation

- Controlled evidence is confined to the TMJ; limb and spine joints in actual
  hEDS patients have only small, uncontrolled case series.
- No adequately powered RCT exists for peripheral-joint regenerative injections
  in hEDS — the clearest gap and the case for future work.

## Limitations

Few studies; small samples; heterogeneity; reliance on public search (a formal
review would query PubMed, Embase, Scopus, Cochrane). Findings are preliminary
and hypothesis-generating.

## Reproducibility

```{r}
sessionInfo()
```
